Diagnosis_Vis

### 2023-04-29 Diagnosis_Vis.Rmd
Figured out how to make long data for diagnosis!

>>>>

```{r}
ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
  coord_flip()
```

```{r}
library(dplyr)
library(tidyr)

Mothership_Current_Long <- Mothership_Diag %>%
  pivot_longer(
    cols=c(Anxiety_C, Mood_C, Substance_C, Trauma_C, Psychotic_C, Eating_C,  Somatic_C),
    names_to = 'disorder_present'
  ) %>%
  filter(value != 0) %>%
  select(!value) %>%
  pivot_longer(
    cols=c(Co_Anx, Co_Mood, Co_OCD, CO_BPD, CO_Psychotic, CO_Eating, CO_Somatic),
    names_to = 'Co_Occuring'
  )%>%
  filter(value != 0) %>%
  select(!value) 
  ## pick back up here!!
    #filter out disorders that are co occuring the same (e.g. anxiety and anxiety)
    #maybe figure out to make a variable that is co-occuring for primary and secondary same thing (e.g. GAD and panic)
  # mutate(

view(Mothership_Current_Long)

                     Mood_D 
                    Anxiety_D 
                #OCD_P is for current OCD
                #BPD_P is for current BPD
                    Substance_D 
                    Trauma_D 
                    Psychotic_D 
                    Eating_D 
                    Somatic_D 
                    Disorder_Type = primary diag 
                  Anxiety_C 
                  Mood_C 
                  Substance_C
                  Trauma_C 
                  Psychotic_C
                  Eating_C 
                  Somatic_C 
                  Emotional_dis 
                  Co_Anx 
                  Co_Mood 
                  Co_OCD
                  CO_BPD 
                  CO_Psychotic
                  CO_Eating 
                  CO_Somatic
